Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-12-01 paper/main.Rmd
adding description of files and objectives

bibliography: bibliography.bib
preamble: >
  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
  \def\mod{~\text{mod}~}
  \newtheorem{definition}{Definition}
  \usepackage{mathptmx}
  \usepackage{caption}
  \usepackage{algorithm, algorithmicx, algpseudocode}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
  \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
output:
  bookdown::pdf_book:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
---

@@

<!-- \begin{algorithm}[!thb] -->
<!-- 	\caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}. -->
<!-- 	\begin{algorithmic}[1] -->
<!-- 		\Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}. -->
<!-- 		\For{$k=1:K$, $j=1:J$} -->
<!-- 		\State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations. -->
<!-- 		\State $d \gets JSD(\tilde{q(v)_{a_{j}b_{k}}},\tilde{q(v)_{a_{j}'b_{k}'}})$ -->
<!-- 		\If {$b_k = b_k'$}  -->
<!-- 		\State $d* \gets \lambda d$  \Comment{upweight within-facet distances} -->
<!-- 		\Else  -->
<!-- 		\State $d* \gets 1/\lambda d $ \Comment{downweight across-facet distances} -->
<!-- 		\EndFor -->
<!-- 		\State Set the raw distance measure as $max(d*)$ where max is taken over all $j, j', k, k'$. -->

<!-- 		\EndProcedure -->
<!-- 	\end{algorithmic} -->
<!-- \end{algorithm} -->

>>>>

bibliography: bibliography.bib
preamble: >
  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
  \def\mod{~\text{mod}~}
  \newtheorem{definition}{Definition}
  \usepackage{mathptmx}
  \usepackage{caption}
  \usepackage{algorithm}
  \usepackage{algorithmicx}
  \usepackage{algpseudocode}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
  \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
output:
  bookdown::pdf_book:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
---

@@

\begin{algorithm}[!thb]
	\caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
	\begin{algorithmic}[1]
		\Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}.
		\For{$k=1:K$, $j=1:J$}
		\State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations.
		\State $d \gets JSD(\tilde{q(v)_{a_{j}b_{k}}},\tilde{q(v)_{a_{j}'b_{k}'}})$
		\If {$b_k = b_k'$}
		\State $d* \gets \lambda d$  \Comment{upweight within-facet distances}
		\Else
		\State $d* \gets 1/\lambda d $ \Comment{downweight across-facet distances}
		\EndFor
		\State Set the raw distance measure as $max(d*)$ where max is taken over all $j, j', k, k'$.

		\EndProcedure
	\end{algorithmic}
\end{algorithm}

### 2020-12-01 paper/main.tex
adding description of files and objectives

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Selecting and ranking interesting pairs of cyclic temporal granularities},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

@@

\hypertarget{notations}{%
\subsubsection{Notations}\label{notations}}

@@

Each of the \(KL\) data subsets in the data structure have multiple observations and may vary widely across different subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain. The set of observations corresponding to each combination is assumed to be a sample from an unknown probability density function.
While the whole population of observations has certain characteristics, we can typically never measure all of them. Often shape, central tendency, and variability are the common characteristics used to describe the distribution. Another way to describe the probability distribution is through quantiles. (Define quantiles here) Sample quantiles could be thought to estimate the population quantiles. But there are a large number of different definitions used for sample quantiles. The median-unbiased estimator is recommended (Rob's paper) because of its desirable properties of a quantile estimator and can be defined independently of the underlying distribution.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Fix harmony pair \((C_i, C_j)\).
\item
  Fix \(k\). Then there are \(L\) groups corresponding to level \(A_k\) of \(C_i\).
\item
  Compute \(m = \binom{L}{2}\) pairwise distances between distributions of \(L\) unordered levels and \(m = L-1\) pairwise distances for \(L\) ordered categories.
\item
  Identify maximum within the \(m\) computed distances.
\item
  Compute maximum distance (\(M\)) using appropriate norming constants.
\item
  Use Steps 1-5 to compute maximum distance for \(\forall k \in \{1, 2, \ldots, K\}\).
\item
  Compute the distance measure MMPD\_raw = median \((M_1, M_2, \dots, M_K)\).
\end{enumerate}

@@

\hypertarget{distribution}{%
\subsubsection{Distribution}\label{distribution}}

@@

@@

{\centering \includegraphics[width=\textwidth]{figure/dist-across-facets-1}

@@

\caption{Distribution of $MMPD_{raw}$ for different facet levels are shown. The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained. }\label{fig:dist-across-facets}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{figure/dist-across-x-1}

@@

@@

@@

\begin{center}\includegraphics[width=\textwidth]{Figs/simulation} \end{center}

Observations from the null distribution are chosen as:\\
\texttt{sim\_norm\_null\ =\ \ \ distributional::dist\_normal(5,\ 10)}~\\
\texttt{sim\_gamma\_null\ \ =\ \ \ distributional::dist\_gamma(0.5,\ 0.2)}~\\

@@

\begin{center}\includegraphics[width=\textwidth]{figure/norm-data, "Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked."-1} \end{center}

@@

{\centering \includegraphics[width=\textwidth]{figure/null-dist-1}

@@

\caption{Distribution of mmpd across different facet levels (columns) and x-axis levels (rows) for null ditribution normal(5,10) and gamma(0.5, 0.2). The distribution of MMPD is unaffected by the null distribution considered. It is also the same across all facet levels but not across the x-axis, which means normalisation is failing across x-axis.}\label{fig:null-dist}
\end{figure}

@@

@@

\hypertarget{algorithm-2}{%
\section{Algorithm}\label{algorithm-2}}

\noindent The algorithm employed for computing MMPD is summarized as follows:

\begin{itemize}
\tightlist
\item
  \textbf{Input:} Data corresponding to all harmony pairs, i.e., data sets of the form \((C_i, C_j, v)\)
  \(\forall i, j \in N_C\)\\
\item
  \textbf{Output:} MMPD (Median Maximum Pairwise Distances) measuring the average variation across different levels of \(C_i\) and \(C_j\) \(\forall i, j \in N_C\)
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Fix harmony pair \((C_i, C_j)\).
\item
  Fix \(k\). Then there are \(L\) groups corresponding to level \(A_k\) of \(C_i\).
\item
  Compute \(m = \binom{L}{2}\) pairwise distances between distributions of \(L\) unordered levels and \(m = L-1\) pairwise distances for \(L\) ordered categories.
\item
  Identify maximum within the \(m\) computed distances.
\item
  Compute normalized maximum distance (\(NM\)) using appropriate norming constants.
\item
  Use Steps 1-5 to compute normalized maximum distance for \(\forall k \in \{1, 2, \ldots, K\}\).
\item
  Compute MMPD = median \((NM_1, NM_2, \dots, NM_K)\)/log(\(K\)).
\item
  Repeat Steps 1 to 7 for all harmony pairs.
\end{enumerate}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Selecting and ranking interesting pairs of cyclic temporal granularities},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

@@

Each of the data subsets in the data structure have multiple observations and may vary widely across different subsets due to the structure of the calendar, missing observations or uneven locations of events in the time domain. The set of observations corresponding to each combination is assumed to be a sample from an unknown probability density function.
While the whole population of observations has certain characteristics, we can typically never measure all of them. Often shape, central tendency, and variability are the common characteristics used to describe the distribution. Another way to describe the probability distribution is through quantiles. (Define quantiles here) Sample quantiles could be thought to estimate the population quantiles. But there are a large number of different definitions used for sample quantiles. The median-unbiased estimator is recommended (Rob's paper) because of its desirable properties of a quantile estimator and can be defined independently of the underlying distribution.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Fix harmony pair \((C_i, C_j)\).
\item
  Fix \(k\). Then there are \(L\) groups corresponding to level \(A_k\) of \(C_i\).
\item
  Compute \(m = \binom{L}{2}\) pairwise distances between distributions of \(L\) unordered levels and \(m = L-1\) pairwise distances for \(L\) ordered categories.
\item
  Identify maximum within the \(m\) computed distances.
\end{enumerate}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\item
  Use Steps 1-4 to compute maximum distance for \(\forall k \in \{1, 2, \ldots, K\}\).
\item
  Compute the distance measure MMPD\_raw = median \((M_1, M_2, \dots, M_K)\).
\end{enumerate}

\begin{algorithm}[!thb]
    \caption{Calculation for a raw distance measure between two cyclic granularities $A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets.}\label{alg:scoreopt}.
    \begin{algorithmic}[1]
        \Procedure{RawMMPD}{$A = \{ a_j: j = 1, 2, \dots, J\}$, $B = \{ b_k: k = 1, 2, \dots, K\}$, $v = \{ v_t: t = 1, 2, \dots, T\}$}.
        \For{$k=1:K$, $j=1:J$}
        \State Find distances between pairs of all possible combinations of categories $(a_jb_k,a_j'b_k')$ by computing JSD between quantiles of the measured variable $q(v)$ across these combinations.
        \State $d \gets JSD(\tilde{q(v)_{a_{j}b_{k}}},\tilde{q(v)_{a_{j}'b_{k}'}})$
        \If {$b_k = b_k'$}
        \State $d* \gets \lambda d$  \Comment{upweight within-facet distances}
        \Else
        \State $d* \gets 1/\lambda d $ \Comment{downweight across-facet distances}
        \EndFor
        \State Set the raw distance measure as $max(d*)$ where max is taken over all $j, j', k, k'$.

        \EndProcedure
    \end{algorithmic}
\end{algorithm}

@@

\hypertarget{behavior-of-raw-distance-measure}{%
\section{Behavior of raw distance measure}\label{behavior-of-raw-distance-measure}}

To understand the behavior of raw MMPD for different parameters \(nperm\) , \(n\) (\(n_x\), \(n_f\) and combination), \(D\) , \(l_x\), \(l_f\) .

\hypertarget{distribution-across-facet-and-x-categories}{%
\subsection{Distribution across facet and x categories}\label{distribution-across-facet-and-x-categories}}

@@

\begin{center}\includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/simulations/result_report/hist_nxbyfacet} \end{center}

\begin{verbatim}
#> [1] "/Users/sgup0008/Documents/paper-hakear"
\end{verbatim}

@@

{\centering \includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/simulations/result_report/nx_by_facet_raw}

@@

\caption{Distribution of $MMPD_{raw}$ for different facet levels are shown. The location of the distribution shifts rightwards implying that as the number of facets increase, it is more likely that a higher value of $MMPD_{raw}$ will be obtained.}\label{fig:dist-across-facets}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/simulations/result_report//nfacet_by_nx_raw}

@@

\hypertarget{distribution-across-different-sample-size}{%
\subsection{Distribution across different sample size}\label{distribution-across-different-sample-size}}

\hypertarget{distribution-across-different-permutation-size}{%
\subsection{Distribution across different permutation size}\label{distribution-across-different-permutation-size}}

\hypertarget{distribution-across-normal-and-non-normal-underlying-distribution}{%
\subsection{Distribution across normal and non-normal underlying distribution}\label{distribution-across-normal-and-non-normal-underlying-distribution}}

@@

\hypertarget{simulation-study-1}{%
\subsection{Simulation study}\label{simulation-study-1}}

@@

\begin{center}\includegraphics[width=\textwidth]{/Users/sgup0008/Documents/paper-hakear/paper/Figs/simulation} \end{center}

Observations from Normal(5, 10) and Gamma(0.5, 0.2) are3 chosen in all the designs.

--\textgreater{}
--\textgreater{}

@@

@@

{\centering \includegraphics[width=\textwidth]{figure/norm-data-1}

@@

\caption{Distribution of $MMPD_{norm}$ across different levels of facet and x-axis. These distributions should look the same if normalisation worked.}\label{fig:norm-data}
\end{figure}

@@

\begin{center}\includegraphics[width=\textwidth]{figure/unnamed-chunk-4-1} \end{center}

@@
